---
output: 
    github_document:
      number_sections: yes
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  eval = FALSE
)
```

# CRAN Submission Checklist {-}

This list mainly comes from the book R Packages and [R Packages (2e)](https://r-pkgs.org/).
<!-- badges: start -->
<!-- badges: end -->

# Checks

```{r}
usethis::proj_set(".")
```


## Local `R CMD check`

```{r}
devtools::check()
```

or press `Ctrl`/`Cmd` + `Shift` + `E`

## Continuous Integration: GitHub Action

```{r}
usethis::use_github_action_check_standard()
```

## R-hub

```{r}
devtools::check_rhub(interactive = FALSE)

rhub::check_with_sanitizers()
```

## Win-Builder

```{r}
devtools::check_win_devel()
devtools::check_win_release()
devtools::check_win_oldrelease()
```


## [Reverse dependencies](https://r-pkgs.org/release.html#release-deps)


# Before Submission

## DESCRIPTION
```{r}
usethis::use_description()
```
### Version 

```
<major>.<minor>.<patch>       (released version)
<major>.<minor>.<patch>.<dev> (dev version)
```


### License 
```{r}
usethis::use_gpl3_license()
```


## README.md

```{r}
usethis::use_readme_rmd()
```

Badge?
```{r}
usethis::use_cran_badge()
```

```
[![R-CMD-check](https://github.com/FinYang/fable.thrreg/workflows/R-CMD-check/badge.svg)](https://github.com/FinYang/fable.thrreg/actions)
[![license](https://img.shields.io/badge/license-GPL--3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0.en.html)
```


## NEWS.md

```{r}
usethis::use_news_md()
```

## cran-comments.md
```{r}
usethis::use_cran_comments()
```

## Spelling

```{r}
devtools::spell_check()
```


## SUBMIT!

```{r}
devtools::release()
```

# After Submission

## Wait patiently

If not, then https://r-hub.github.io/cransays/articles/dashboard.html

## Commit CRAN-SUBMISSION

## GitHub release

* Release on Github with tag version v1.2.3
* Copy NEWS to release notes.

## Bump dev version

* Delete CRAN-SUBMISSION
* Bump to version .9000 in DESCRIPTION
* Add a heading in NEWS
* Commit

```{r}
usethis::use_dev_version()
```

